Relationship Between Common Stream Health Indicators

### 2021-12-10 products/manuscript/Manuscript.Rmd
Misc. Edits - CC

4. Use NA assessment to see determine which variables to remove from assessment. This was done using the is_na function. Several of the columns have more than half of the data missing. This is pretty common for citizen science data, seeing as collection is opportunistic. As such, I decided to remove P04 and temperature, because they are missing a lot of data. Finally, I decided to remove all missing values and see the condition of the data knowing that there are now no missing values. I removed NA data using the na.omit() function.

@@

Focusing on just biological score as the outcome variable biological score (figures 1-3 below), the interaction with conductivity was determined to be negative for the MIDO and NORO site. However, the BICO site had a positive interaction. Next, the regression plotting found a negative interaction with E. coli cfu for the MIDO and BICO sites. But, there was a positive interaction for the NORO site. For nitrate concentration, the interaction was negative for all sites. Finally, the interaction with turbidity was negative for the BICO site, while a positive interaction was found for the MIDO and NORO sites.

@@

Focusing on E. coli cfu as the outcome of interest (figures 4-6 below), the interaction with conductivity was negative for MIDO and NORO. However, the BICO site had a positive interaction. The interaction with nitrate concentration was negative for all three sites. Finally the interaction with turbidity was positive at all three sites.

>>>>

4. Use NA assessment to see determine which variables to remove from assessment. This was done using the is_na() function. Several of the columns have more than half of the data missing. This is pretty common for citizen science data, seeing as collection is opportunistic. As such, I decided to remove phosphate ([PO4]) and temperature, because they are missing a lot of data. Finally, I decided to remove all missing values and see the condition of the data knowing that there are now no missing values. I removed NA data using the na.omit() function.

@@

Focusing on just biological score as the outcome variable biological score (Figures 1-3 below), the interaction with conductivity was determined to be negative for the MIDO and NORO site. However, the BICO site had a positive interaction. Next, the regression plotting found a negative interaction with E. coli cfu for the MIDO and BICO sites. But, there was a positive interaction for the NORO site. For nitrate concentration, the interaction was negative for all sites. Finally, the interaction with turbidity was negative for the BICO site, while a positive interaction was found for the MIDO and NORO sites.

@@

Focusing on E. coli cfu as the outcome of interest (Figures 4-6 below), the interaction with conductivity was negative for MIDO and NORO. However, the BICO site had a positive interaction. The interaction with nitrate concentration was negative for all three sites. Finally the interaction with turbidity was positive at all three sites.
